Towards Reliable Machine Learning Deployments in the Cloud

### 2023-12-11 plots/cifar/aft_comparison.tex
update data/plots

\begin{table}
\caption{Comparison of AFR Models on the CIFAR dataset.}
\label{tab:cifar}
\begin{tabular}{llrlrr}
\toprule
 & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t;\theta)$ \\
\midrule
weibull & -2992.60 & 0.91 & -2992.60 & 0.09 & 0.08 \\
cox & -- & 0.92 & -- & 0.03 & 0.08 \\
log_logistic & -3173.60 & 0.92 & -3173.60 & 0.09 & 0.08 \\
log_normal & -3072.67 & 0.92 & -3072.67 & 0.09 & 0.08 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\caption{Comparison of AFR Models on the CIFAR dataset.}
\label{tab:cifar}
\begin{tabular}{llrlrr}
\toprule
 & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t;\theta)$ \\
\midrule
weibull & -472.03 & 0.83 & -472.03 & 0.25 & 0.22 \\
cox & -- & 0.83 & -- & 0.20 & 0.25 \\
log_logistic & -514.66 & 0.83 & -514.66 & 0.25 & 0.21 \\
log_normal & -518.86 & 0.83 & -518.86 & 0.26 & 0.22 \\
\bottomrule
\end{tabular}
\end{table}

### 2023-12-11 plots/cifar100/aft_comparison.tex
update data/plots

\begin{table}
\caption{Comparison of AFR Models on the CIFAR100 dataset.}
\label{tab:cifar100}
\begin{tabular}{llrlrr}
\toprule
 & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t;\theta)$ \\
\midrule
weibull & -3092.89 & 0.93 & -3092.89 & 0.13 & 0.09 \\
cox & -- & 0.97 & -- & 0.09 & 0.09 \\
log_logistic & -3817.38 & 0.96 & -3817.38 & 0.12 & 0.09 \\
log_normal & -3315.07 & 0.96 & -3315.07 & 0.12 & 0.09 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\caption{Comparison of AFR Models on the CIFAR100 dataset.}
\label{tab:cifar100}
\begin{tabular}{llrlrr}
\toprule
 & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t;\theta)$ \\
\midrule
weibull & -329.38 & 0.83 & -329.38 & 0.33 & 0.18 \\
cox & -- & 0.84 & -- & 0.24 & 0.16 \\
log_logistic & -353.45 & 0.84 & -353.45 & 0.31 & 0.17 \\
log_normal & -355.45 & 0.84 & -355.45 & 0.31 & 0.17 \\
\bottomrule
\end{tabular}
\end{table}

### 2023-12-11 plots/mnist/aft_comparison.tex
update data/plots

\begin{table}
\caption{Comparison of AFR Models on the MNIST dataset.}
\label{tab:mnist}
\begin{tabular}{llrlrr}
\toprule
 & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t;\theta)$ \\
\midrule
weibull & -2908.50 & 0.95 & -2908.50 & 0.06 & 0.06 \\
cox & -- & 0.96 & -- & 0.03 & 0.06 \\
log_logistic & -3089.51 & 0.96 & -3089.51 & 0.06 & 0.06 \\
log_normal & -3077.18 & 0.96 & -3077.18 & 0.06 & 0.06 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\caption{Comparison of AFR Models on the MNIST dataset.}
\label{tab:mnist}
\begin{tabular}{llrlrr}
\toprule
 & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t;\theta)$ \\
\midrule
weibull & -606.12 & 0.78 & -606.12 & 0.23 & 0.22 \\
cox & -- & 0.78 & -- & 0.18 & 0.22 \\
log_logistic & -606.18 & 0.78 & -606.18 & 0.22 & 0.22 \\
log_normal & -616.30 & 0.78 & -616.30 & 0.23 & 0.22 \\
\bottomrule
\end{tabular}
\end{table}
